\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{black}
\nopagenumbers{}

\usepackage[scale=0.9]{geometry}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage[unicode,hidelinks]{hyperref}

\setlist[itemize]{leftmargin=*, itemsep=0.1em}

\name{Abderrahmane}{Ouroui}
\address{Casablanca, Morocco}{}{}
\email{abdououroui123@gmail.com}

\begin{document}
\makecvtitle

\vspace{-8mm}
\begin{center}
\textbf{DevOps Engineer II | Platform Engineer} \\
\href{https://www.linkedin.com/in/abderrahmane-ouroui-5b73b1216/}{linkedin.com/in/abderrahmane-ouroui-5b73b1216} |
\href{https://github.com/webfordata}{github.com/webfordata} |
\href{https://leetcode.com/webfordata/}{leetcode.com/webfordata}
\end{center}

% =====================
\section{Professional Summary}

DevOps Engineer II / Platform Engineer building reliable production runways on OCI with Terraform, Kubernetes (OKE), secure networking, observability, CI/CD, and MLOps-ready foundations. OCI is my strongest production platform; the engineering standards I apply are cloud-portable across provider primitives, including Infrastructure as Code, least-privilege IAM, Kubernetes runtime patterns, CI/CD promotion, observability, cost awareness, and production governance. Target roles include OCI Platform Engineer, DevOps Engineer, Platform Engineer, and Kubernetes / MLOps Platform Engineer.

% =====================
\section{Experience}

\cventry{2023--Present}{DevOps Engineer II / Platform Engineer}{Oracle}{Casablanca, Morocco}{}{
\begin{itemize}
\item Own OCI-native platform architecture across development, test, stage, and production environments.
\item Refactored and migrated Terraform infrastructure while protecting \textbf{500+ OCI resources per environment} from unnecessary recreation.
\item Built reviewable release paths using Terraform boundaries, IAM guardrails, environment promotion checks, and production validation.
\item Designed secure networking paths across load balancers, API gateways, reverse proxies, Kubernetes services, application platforms, and third-party authN/authZ flows.
\item Deployed and operated Kubernetes clusters on OKE, improving scalability, resilience, and high availability for containerized workloads.
\item Managed release lifecycle from development to production, including deployment validation, rollback planning, and post-release monitoring.
\item Improved incident detection and triage using OCI Logging, OCI Monitoring, Grafana dashboards, alarms, and operational runbooks.
\item Improved platform scalability, performance, and cost efficiency through architecture, configuration, and resource optimization.
\item Automated provisioning, orchestration, deployment, scaling, and management of containerized workloads.
\item Supported Beta programs, technical workshops, and POCs while contributing to delivery of the team’s \textbf{first GA product}.
\item Owned production operations, troubleshooting platform issues, and improving reliability across environments.
\item Mentored team members and supported onboarding, knowledge sharing, troubleshooting, and platform adoption by other teams.
\item Enabled AI-ready data foundations using OCI Data Science, MLflow, Object Storage, Data Flow, Spark, and model artifact workflows.
\end{itemize}
}

\cventry{2023}{Research Assistant}{Oracle}{Casablanca, Morocco}{}{
Delivered backend services and CI/CD workflows using Java, Groovy, Gradle, Jenkins, GitLab, JUnit, and Mockito.
}

\cventry{2022}{Full Stack Developer}{diaaland}{}{}{
Built product workflows and third-party integrations across NestJS, MongoDB, React, Strava, and Garmin.
}

\cventry{2021}{Web Developer}{INTELLCAP SARL}{}{}{
Delivered marketplace-style web functionality using React, GraphQL, PHP, and WooCommerce.
}

% =====================
\section{Technical Skills}

\cvitem{Cloud}{Oracle Cloud Infrastructure, OKE, Compute, VCN, Load Balancer, API Gateway, IAM, Object Storage, Block Volume, Autonomous Database, OCI Logging, OCI Monitoring}
\cvitem{DevOps}{Terraform, Infrastructure as Code, Kubernetes, Docker, CI/CD, GitLab, Jenkins, artifact delivery, release management, rollback planning}
\cvitem{Operations}{Linux, secure networking, NSGs, Traefik, observability, Grafana, incident response, production operations, high availability, cost optimization}
\cvitem{Cloud-Portable Standards}{Infrastructure as Code, least-privilege IAM, Kubernetes runtime patterns, CI/CD promotion gates, observability, cost awareness, production governance}
\cvitem{Databases}{Oracle Database, Autonomous Database, MySQL, MongoDB}
\cvitem{AI/MLOps}{OCI Data Science, OCI Data Flow, Spark, PySpark, MLflow, OCI AI Services, model artifacts, MLOps foundations, AI integration}

% =====================
\section{Certifications}

\cvitem{}{
\href{https://catalog-education.oracle.com/ords/certview/sharebadge?id=5DCB8BDEE987AB0D33F444C6F0144AEC8E9596EF9BA9A3528575CBDC6F3F67AE}
{Oracle Cloud Infrastructure 2025 Certified Architect Associate}
}

\cvitem{}{
\href{https://catalog-education.oracle.com/ords/certview/sharebadge?id=703518BB3025293CEBF2E2E2207E532FEF6B4989E515803FA6B2A07A3956C00F}
{Oracle Cloud Infrastructure 2024 Certified Foundations Associate}
}

\cvitem{}{
\href{https://www.coursera.org/account/accomplishments/certificate/SD425CFMRN48}
{Building Scalable Java Microservices with Spring Boot and Spring Cloud -- Google}
}

% =====================
\section{Education}

\cventry{2020--2023}{Engineering Degree in Computer Science}{ENSIAS}{Morocco}{}{
National School of Computer Science and Systems Analysis.
}

\cventry{2017--2019}{Preparatory Classes in Mathematics}{CPGE}{Morocco}{}{}

% =====================
\section{Languages}

\cvitem{}{Arabic, English, French}

\end{document}
